\section{Findings}
%interesting findings?
%obstacles? solutions/workarounds/attempts?
During the first five weeks of the term, we uncovered some interesting issues with our project.
First, we found some inconsistencies within our dataset.
In addition to trivial errors such as edge weights without edge definitions--which we ignore--
we found and addressed the following issues:
\begin{enumerate}
\item \emph{Duplicate vertices with different confidence values.} This is likely due to degrading confidence over time,
and therefore we use the lowest (most recent) confidence value and will investigate next week.
\item \emph{Hard constraints, representing manually verified facts.} We give these vertices a confidence value of 1,
and note that we will have to address hard constraints in our inference algorithm.
\item \emph{Conflicting beliefs $x$ and $\neg x$.} The vertex datasets contain a probability distribution of all possible values
(in our case, true or false).  We simply combine the conflicting beliefs into a single entry, and give precedence
to hard constraints as above.
\item \emph{Existing edge data containing non-existent vertices.} This is caused by manually verified facts about
vertices that do not exist in the knowledge base. We subsequently ignore them.
\end{enumerate}

Our results from the initial test look promising.
Our corrected knowledge base shows considerable updates of confidence values,
and we observe increases in confidence values on verifiably correct beliefs.
We have also observed a few decreases in confidence values that are questionable,
and will look into these cases in the beginning of next week.
